\input{mmd-manuscript-header  }
\def\mytitle{Novel Manuscript Format  }
\def\myauthor{Matt Carless  }
\def\address{Every manuscript should  \\
have your address and  \\
contact details on the title page only.  \\
}
\def\agent{An agent's address can be  \\
included underneath if you  \\
have one.  \\
}
\def\surname{Carless  }
\def\comment{Based on the information found at the BBC  \\
http:\slash \slash www.bbc.co.uk\slash writersroom\slash scriptsmart\slash formats.shtml  \\
Sample text from that same web site  \\
}
\input{mmd-manuscript-begin-doc  }
\chapter{CHAPTER ONE}
\label{chapterone}

This standard manuscript format is required for prose
fiction so that work can be easily read and edited by
editors and copy editors. It also allows editors to both
estimate the word count and accurately determine how many
pages will be required to produce a book using the page
size, style, and type font of their choice.

Manuscripts for full-length novels require a separate
title page. The author's real name and address, telephone
number and e-mail address should be shown in the upper left
corner of the first page, single-spaced. The title of the
story appears in all capitals about half way down the page.
The author's name follows the title on the by-line and
should be shown as the author wants it to appear when
published. A real name, or pseudonym may be used and may
include initials or actual given name, and professional
designation.

All text should be double-spaced and flush-left, not
justified, with a ``ragged'' right margin. All paragraphs are
indented by five spaces and not separated by an additional
blank line. Each sentence should end with two spaces.

Top and bottom margins must be set to allow for 25
lines of text to the page (not including the page header).
Left and right margins must be set to allow for an average
of 10 words to a line in order to accurately assess the
final word count. In publishing terms, one ``word'' equals
six characters (including punctuation and spaces), thus each
line of text must allow for a maximum of 60 characters of
text.

Each page, except the title page, must include a header
consisting of the author's real surname, the title of the
work (or a keyword) in capitals, and the page number.

\section{Scene}
\label{scene}

Scene breaks are indicated like this. Do not simply
add an extra line space as this can be missed by the
typesetter. Indicate \emph{italics} by \emph{underlining}. 

\chapter{CHAPTER TWO}
\label{chaptertwo}

Begin each new chapter on a new page like this with the
chapter number about a third of the way down the page. 

Writers should never use the word-count feature of
their computers to determine the number of words in a
manuscript. The term \emph{word count}, as used in the publishing
industry, is actually inaccurate. Editors count pages, not
words. Properly prepared manuscripts, with 25 lines of type
to a page and an average of 10 words to a line are assumed
to contain 250 words on each full page. Partial pages,
where the text covers half or less of the available space,
are counted as 125 words for the publishers purposes, except
for the first pages of chapters or short stories which are
counted as full pages. Once the initial word-count has been
calculated, it should be rounded up to the nearest 1000
words (100 for short stories). 

\input{mmd-memoir-footer.tex  }

\end{document}
